---
title: "MRMS:MultiQPE/QPE"
author: "Megan Sears"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(
  echo = F,
  message = F, 
  warning  = F)

# load packages
library(R.utils) #to unzip the gz files
library(tidyverse)
library(lubridate)
library(raster)
library(rgdal)
library(sf)
library(sp)
library(mapview)
library(terra)
library(tmap)
library(readr)
library(gridExtra)
library(ggplot2); theme_set(theme_bw(base_size = 16))
library(here)
library(irr)
library(plotly)
library(kableExtra)
library(dataRetrieval)

```

Create a bounding box to crop for multi-QPE and QPE rasters

```{r}

# ETF watersheds - don't need right now
et_sheds <- vect('./data/watershed_bnd_UTM.shp') %>%
  terra::project(., 'EPSG:26913')

# all rain sensors for CPF, ETF, Bennett
rain <- read_csv('./data/sensor_coords.csv') %>%
  filter(type == 'rain') %>%
  drop_na(y) %>%
  st_as_sf(coords = c('x', 'y'), crs = 4326) %>%
  st_transform(crs = st_crs(et_sheds))

# bounding box based on rain sensors to crop MRMS data
bbox <- st_bbox(rain)

# bounding box cuts off some points, so expand it
xrange <- bbox$xmax - bbox$xmin # range of x values
yrange <- bbox$ymax - bbox$ymin # range of y values

bbox[1] <- bbox[1] - (0.1 * xrange) # xmin - left
bbox[3] <- bbox[3] + (0.1 * xrange) # xmax - right
bbox[2] <- bbox[2] - (0.1 * yrange) # ymin - bottom
bbox[4] <- bbox[4] + (0.1 * yrange) # ymax - top

#mapview(bbox)
```

# 1. MutliQPE/QPE
Need to divide MultiQPE by QPE to get the correction used

(below is a test and/or example)

```{r}

#pull in raster
multi <- rast('/Users/megansears/Documents/MRMS/MultiSensor/2021/MultiSensor_QPE_01H_Pass2_00.00_20210814-220000.grib2') %>%
  terra::project(., 'EPSG:26913')

#crop raster to cpf
multi <- terra::crop(multi, ext(bbox)) #this came from other script rn

plot(multi)

qpe <- rast('/Users/megansears/Documents/MRMS/QPE/2021/RadarOnly_QPE_01H_00.00_20210814-220000.grib2') %>%
  terra::project(., 'EPSG:26913')

#crop raster to cpf
qpe <- terra::crop(qpe, ext(bbox)) #

plot(qpe)

test <- multi / qpe

test <- classify(test, cbind(NA, 1))
plot(test)

test <- raster(test)

mapview(test)

```

## 2021

```{r}

# Set the working directory to the folder containing your rasters
setwd("/Users/megansears/Documents/MRMS")

# Retrieve the file names of the rasters in each folder
folder1_rasters <- list.files("./MultiSensor/2021", pattern = ".grib2", full.names = TRUE)
folder2_rasters <- list.files("./QPE/2021", pattern = "grib2", full.names = TRUE)

# Define a function to perform the division operation and save the result
perform_division <- function(raster1, raster2, result_folder) {
  
  # Extract the last 15 digits from the file name (datetime)
  last_21_digits1 <- substring(basename(raster1), max(nchar(basename(raster1)) - 20, 1))
  last_21_digits2 <- substring(basename(raster2), max(nchar(basename(raster2)) - 20, 1))
  
  if (last_21_digits1 == last_21_digits2) {
    r1 <- rast(raster1) %>%
      terra::project(., 'EPSG:26913')
    
    r1 <- terra::crop(r1, ext(bbox))
    
    r2 <- rast(raster2) %>%
      terra::project(., 'EPSG:26913')
    
    r2 <-  terra::crop(r2, ext(bbox))
    
    result_raster <- r1 / r2 #divde Multi / QPE
    
    result_raster <-
      classify(result_raster, cbind(NA, 1)) # if NA change to 1 (means no diff in precip bc 0/0)
    
    # Save the resulting raster
    output_file <-
      file.path(result_folder, paste0("result_", last_21_digits1, ".tif"))
    
    writeRaster(result_raster, output_file, overwrite = TRUE)
  }
}

# Apply the function to each pair of matching rasters
result_folder <- "./MultiSensor_QPE_divide"  # Path to the folder to store the resulting rasters

# Find matching rasters and perform division using lapply and mapply
lapply(folder1_rasters, function(raster1) {
  # Extract the last 21 digits from the file name of raster1
  last_21_digits1 <- substring(basename(raster1), max(nchar(basename(raster1)) - 20, 1))
  
  # Find matching rasters in folder2
  matching_rasters <- grep(last_21_digits1, folder2_rasters, value = TRUE)
  
  # Perform division for each matching raster
  mapply(perform_division, raster1, matching_rasters, MoreArgs = list(result_folder = result_folder))
})

```

## 2022

```{r}

# Set the working directory to the folder containing your rasters
setwd("/Users/megansears/Documents/MRMS")

# Retrieve the file names of the rasters in each folder
folder1_rasters <- list.files("./MultiSensor/2022", pattern = ".grib2", full.names = TRUE)
folder2_rasters <- list.files("./QPE/2022", pattern = "grib2", full.names = TRUE)

# Define a function to perform the division operation and save the result
perform_division <- function(raster1, raster2, result_folder) {
  
  # Extract the last 15 digits from the file name (datetime)
  last_21_digits1 <- substring(basename(raster1), max(nchar(basename(raster1)) - 20, 1))
  last_21_digits2 <- substring(basename(raster2), max(nchar(basename(raster2)) - 20, 1))
  
  if (last_21_digits1 == last_21_digits2) {
    r1 <- rast(raster1) %>%
      terra::project(., 'EPSG:26913')
    
    r1 <- terra::crop(r1, ext(bbox))
    
    r2 <- rast(raster2) %>%
      terra::project(., 'EPSG:26913')
    
    r2 <-  terra::crop(r2, ext(bbox))
    
    result_raster <- r1 / r2 #divde Multi / QPE
    
    result_raster <-
      classify(result_raster, cbind(NA, 1)) # if NA change to 1 (means no diff in precip bc 0/0)
    
    # Save the resulting raster
    output_file <-
      file.path(result_folder, paste0("result_", last_21_digits1, ".tif"))
    
    writeRaster(result_raster, output_file, overwrite = TRUE)
  }
}

# Apply the function to each pair of matching rasters
result_folder <- "./MultiSensor_QPE_divide"  # Path to the folder to store the resulting rasters

#mapply(perform_division, folder1_rasters, folder2_rasters, MoreArgs = list(result_folder = result_folder))



# Find matching rasters and perform division using lapply and mapply
lapply(folder1_rasters, function(raster1) {
  # Extract the last 21 digits from the file name of raster1
  last_21_digits1 <- substring(basename(raster1), max(nchar(basename(raster1)) - 20, 1))
  
  # Find matching rasters in folder2
  matching_rasters <- grep(last_21_digits1, folder2_rasters, value = TRUE)
  
  # Perform division for each matching raster
  mapply(perform_division, raster1, matching_rasters, MoreArgs = list(result_folder = result_folder))
})

```

Get rid of .grib2 from all the filenames

```{r}

# setwd('/Users/megansears/Documents/MRMS')
# 
# # Set the directory path where your files are located
# dir <- './divide_temp'
# 
# # Get the list of files in the directory
# file_list <- list.files(dir)
# 
# # Define a function to rename the files
# rename_files <- function(file) {
#   new_name <- gsub(".grib2", "", file)
#   file.rename(file.path(dir, file), file.path(dir, new_name))
# }
# 
# # Use lapply to apply the renaming function to each file
# lapply(file_list, rename_files)

```

# 2. Resample the divide result to 2-min 

Repeat this chunk for 2021 and 2022

```{r}

setwd('/Users/megansears/Documents/MRMS/MultiSensor_QPE_divide')

# Set the original raster filename
original_file <- "result_20220501-000000.tif"

# Set the destination directory where the files will be copied
destination_directory <- "/Users/megansears/Documents/MRMS/MultiSensor_QPE_divide/2min"

# Extract the base filename without the extension
basename <- tools::file_path_sans_ext(original_file)

# Define the date range (e.g., from June 1 to June 3)
start_date <- as.Date("2022-05-01")
end_date <- as.Date("2022-11-01")

# Generate the date range as a character vector
dates <- as.character(seq(start_date, end_date, by = "day"))

# Define the hour range (e.g., from 0 to 23)
start_hour <- 0
end_hour <- 23

# Generate all the date-time combinations
datetime <- expand.grid(date = dates,
                        hour = sprintf("%02d", seq(start_hour, end_hour)),
                        minute = sprintf("%02d", seq(0, 58, by = 2)))

# Create the new filenames for each date-time combination using lapply
new_filenames <- lapply(1:nrow(datetime), function(i) {
  date <- datetime$date[i]
  hour <- datetime$hour[i]
  minute <- datetime$minute[i]
  new_filename <- paste0("result_", date, "-", hour, minute, ".tif")
  file.path(destination_directory, new_filename)
})

# Create the destination directory if it doesn't exist
if (!dir.exists(destination_directory)) {
  dir.create(destination_directory, recursive = TRUE)
}

# Copy the original raster file to the new filenames using lapply
lapply(new_filenames, function(to) {
  file.copy(original_file, to)
})

```

# 3. Multiple the 2-min correction by the SPR product

Pre-processing below

```{r}
# Below chunk was to move at the files into one folder instead of separated by year
# # Set the source and destination folders
# source_folder <- "/Users/megansears/Documents/MRMS/SPR/2021"
# destination_folder <- "/Users/megansears/Documents/MRMS/SPR"
# 
# # Get the list of files in the source folder
# files <- list.files(source_folder)
# 
# # Move each file to the destination folder
# for (file in files) {
#   source_path <- file.path(source_folder, file)
#   destination_path <- file.path(destination_folder, file)
#   
#   file.rename(source_path, destination_path)
# }

# unzip all grib2.gz (only do this once) - this is for the SPR
# zip <- list.files(path = '/Users/megansears/Documents/MRMS/SPR', pattern = '.gz',
#                   full.names = T)
# 
# #unzip all listed files
# unzip <- lapply(zip, gunzip)

# need to remove the extra hyphens in the data of the 2min divid result rasters
# Set the folder path
folder_path <- "/Users/megansears/Documents/MRMS/MultiSensor_QPE_divide/2min"

# Get the list of files in the folder
# files <- list.files(folder_path, pattern = "*.tif", full.names = TRUE)
# 
# # Rename each file with modified name
# for (file in files) {
#   file_name <- basename(file)
#   new_file_name <- gsub("^([^\\-]+)-([^\\-]+)-", "\\1\\2", file_name)
#   new_file_path <- file.path(dirname(file), new_file_name)
#   
#   file.rename(file, new_file_path)
# }

```

More pre-processing: project and crop the 2-min SPR and save as tif so it can be multiplied by the correction later

Trying my hand at parallel processing

```{r}

library(terra)
library(foreach)
library(doParallel)
library(magrittr)
#library(parallel)

# Set the folder path
folder_path <- "/Users/megansears/Documents/MRMS/SPR"

# Get the list of GRIB2 files in the folder
files <- list.files(folder_path, pattern = "*.grib2", full.names = TRUE)

# Set the number of cores to use (adjust according to your system)
num_cores <- 6

# Initialize parallel processing
cl <- makeCluster(num_cores)
registerDoParallel(cl)

# Define a function to process a single GRIB2 file
process_file <- function(file) {
  # Read the GRIB2 file as a raster
  r <- rast(file) %>%
    project('EPSG:26913')
  
  # Crop the raster
  r <- crop(r, ext(bbox))
  
  # Save the raster as .tif
  new_file_name <- paste0(tools::file_path_sans_ext(basename(file)), "_processed.tif")
  new_file_path <- file.path(folder_path, new_file_name)
  writeRaster(r, filename = new_file_path, overwrite = TRUE)
  
  # Remove unnecessary objects
  rm(r)
}

# Use parallel processing with foreach
foreach(file = files, .packages = c("terra", "magrittr")) %dopar% {
  process_file(file)
}

# Stop parallel processing
stopCluster(cl)


```


