---
title: "mrms spatial"
author: "Megan Sears"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(
  echo = F,
  message = F, 
  warning  = F)

# load packages
library(here)
library(tidyverse)
library(lubridate)
library(zoo)
library(terra)
library(stars)
library(tmap)
library(sf)
library(mapview)
library(zoo)
library(ggspatial)
library(beepr)

```

# Load data and create raster stack by year

```{r}
# read in fire boundaries
et <- st_read("./data/GIS/burn_boundaries/co4020310623920201014_20200904_20210907_burn_bndy.shp")
cp <- st_read('./data/GIS/burn_boundaries/co4060910587920200813_20180915_20210907_burn_bndy.shp')

# look at hads
hads <- read_csv('/Users/megansears/Desktop/temp/hads_locations.csv')

hads1 <- vect(hads, geom = c("longitude_d", "latitude_d"), crs = "EPSG:4326")
hads1 <- as(hads1, 'Spatial')

#
fires <- rbind(et, cp)

mapview(fires) + mapview(hads1)
#
# fires_stars <- st_as_stars(fires)
# 
# # List all the files in the directory
# filenames <- list.files("/Users/megansears/Documents/MRMS/bbox_2fires/2min_2021", pattern = ".tif", full.names = TRUE)
# 
# datetime <- list.files("/Users/megansears/Documents/MRMS/bbox_2fires/2min_2021", pattern = ".tif", full.names = F)
# 
# timestamps <- substr(datetime, 12, 26)
# datetime_seq <- ymd_hms(timestamps) - (7 * 60 * 60)
# 
# # Read all raster files and stack them together
# stack <- read_stars(filenames, along = 3)
# 
# # Set the datetime dimension of the stack
# stack_date <- st_set_dimensions(stack, 3, values = datetime_seq, names = "datetime")
# 
# # Filter the stack_date object by datetime
# stack2021 <- stack_date %>%
#   setNames('MI2_mmhr') %>%
#   mutate(p_mm =  MI2_mmhr*(1/30)) %>%
#   dplyr::select(-MI2_mmhr) %>%
#   filter(datetime > ymd_hms('2021-05-31 23:58:00'),
#          datetime < ymd_hms('2021-09-30 23:58:00'))
# 
# rm(stack, stack_date)
# 
# #save.image("/Users/megansears/Documents/Repos/post-fire_rainfall/bbox_2fires/stack_2023.RData")
# #save.image("/Users/megansears/Documents/Repos/post-fire_rainfall/bbox_2fires/stack_2022.RData")
# #save.image("/Users/megansears/Documents/Repos/post-fire_rainfall/bbox_2fires/stack_2021.RData")

```

# Filter out <0.1 mm

```{r}
# 
# new_crs <- st_crs(4326)
# 
# fires <- st_transform(fires, crs = new_crs)
# 
# # first filter a smaller area so I can work with it easier
# stack23_crop <- st_crop(stack2023, cp)

# filter less than 1
filter_function <- function(x) {
  x[x < 0.1] <- 0
  return(x)
}

# Load your data
load('./data/mrms_data/bbox_2fires/stack_2023.RData')

# Use st_apply with future.apply for parallel processing
stack2023_fil.1 <- st_apply(
  stack2023,
  MARGIN = c("x", "y", "datetime"),
  FUN = filter_function
)

# Beep when done
beep(sound=8)

# Clean up
rm(stack2023)

save.image("./data/mrms_data/bbox_2fires/stack_2023_fil01.RData")
rm(list = ls())

# now do 2022
load("./data/mrms_data/bbox_2fires/stack_2022.RData")

# filter out values less than 1 mm
stack2022_fil.1 <- st_apply(
  stack2022,
  MARGIN = c("x", "y", "datetime"),  # dimensions
  FUN = filter_function
)
rm(stack2022)

save.image("./data/mrms_data/bbox_2fires/stack_2022_fil01.RData")

rm(list = ls())

# 2021
load("./data/mrms_data/bbox_2fires/stack_2021.RData")

# filter out values less than 1 mm 
stack2021_fil01 <- st_apply(
  stack2021,
  MARGIN = c("x", "y", "datetime"),  # dimensions
  FUN = filter_function
)
rm(stack2021)

save.image("./data/mrms_data/bbox_2fires/stack_2021_fil01.RData")

```

# Get stacks to 10 min

## Left

```{r}
year <- 23

#load in stack
load(paste0('./data/mrms_data/bbox_2fires/stack_20', year, '_fil01.Rdata'))

# Construct the original object name
long_name <- paste0('stack20', year, '_fil.1')

# Retrieve the existing object by its name
stack <- get(long_name)

rm(list = long_name)

# set crs
st_crs(stack) <- "+proj=longlat +datum=WGS84"

# bbox of the whole area
bbox <- st_bbox(stack)

# Extract bbox coords
xmin <- bbox['xmin']
xmax <- bbox['xmax']
ymin <- bbox['ymin']
ymax <- bbox['ymax']

# Calculate mid_x
mid_x <- as.numeric(xmin + (xmax - xmin) / 2)

# bbox left site
left_bbox <- st_bbox(c(xmin = as.numeric(xmin), 
                       xmax = mid_x, 
                       ymin = as.numeric(ymin), 
                       ymax = as.numeric(ymax)), 
                     crs = st_crs(4326))

# Crop the left half
left_half <- st_crop(stack, y = left_bbox) 

rm(stack)

# make df
tibble <- as_tibble(left_half)
rm(left_half)
gc()

# aggregate to 10 min
stack10 <- tibble %>%
  mutate(datetime_round = ceiling_date(datetime, "10 mins")) %>%
  group_by(x, y, datetime_round) %>%
  rename(p_mm = filter_function) %>%
  summarize(p_mm = sum(p_mm)) %>%
  drop_na(p_mm)

write_csv(stack10, paste0('./data/mrms_data/bbox_2fires/mrms20', year, '_10min_left.csv'))

```

## Right 

```{r}

#load in stack
load(paste0('./data/mrms_data/bbox_2fires/stack_20', year, '_fil01.Rdata'))

# Construct the original object name
long_name <- paste0('stack20', year, '_fil01')

# Retrieve the existing object by its name
stack <- get(long_name)

rm(list = long_name)

# set crs
st_crs(stack) <- "+proj=longlat +datum=WGS84"

# bbox RIGHT site
right_bbox <- st_bbox(c(xmin = mid_x, 
                       xmax = as.numeric(xmax), 
                       ymin = as.numeric(ymin), 
                       ymax = as.numeric(ymax)), 
                     crs = st_crs(4326))

# Crop the right half
right_half <- st_crop(stack, y = right_bbox)

rm(stack)

# make df
tibble <- as_tibble(right_half)
rm(right_half)
gc()

# aggregate to 10 min
stack10 <- tibble %>%
  mutate(datetime_round = ceiling_date(datetime, "10 mins")) %>%
  group_by(x, y, datetime_round) %>%
  rename(p_mm = filter_function) %>%
  summarize(p_mm = sum(p_mm)) %>%
  drop_na(p_mm)

write_csv(stack10, paste0('./data/mrms_data/bbox_2fires/mrms20', year, '_10min_right.csv'))

```

# MI60

The stack (or tibble) is too large, exhausts memory. The raster stacks need to be cut in half down the middle.

## Left half first

```{r}

year <- 21

stack10 <- read_csv(paste0('./data/mrms_data/bbox_2fires/mrms20', year, '_10min_left.csv'))

# calculates max MI60 over a summer
compute_MI60 <- function(df) {
  # Calculate the rolling sum over 6 intervals (60 minutes)
  rolling_sums <- rollapply(df, width = 6, FUN = sum, na.rm = TRUE, fill = NA, align = "right")
  # Find the max of rolling sums
  max(rolling_sums, na.rm = TRUE)
}

# Calculate MI60 for each pixel over the 10-min data
stack_mi60 <- stack10 %>%
  group_by(x, y) %>%
  arrange(datetime_round) %>%
  mutate(MI60 = compute_MI60(p_mm)) %>%
  summarize(maxMI60 = max(MI60, na.rm = TRUE))

# convert back to stars
stack_intens.1 <- st_as_stars(stack_mi60, dims = c("x", "y"))

# set the crs
st_crs(stack_intens.1) <- st_crs("+proj=longlat +datum=WGS84")

# export as tif
write_stars(stack_intens.1, paste0('./data/mrms_data/bbox_2fires/mi60_', year, '_left01.tif'))

# remove old objects
rm(stack_intens.1, stack10, stack_mi60)

```

## Right half

```{r}

stack10 <- read_csv(paste0('./data/mrms_data/bbox_2fires/mrms20', year, '_10min_right.csv'))

# Calculate MI60 for each pixel over 10-min timesteps
stack_mi60 <- stack10 %>%
  group_by(x, y) %>%
  arrange(datetime_round) %>%
  mutate(MI60 = compute_MI60(p_mm)) %>%
  summarize(maxMI60 = max(MI60, na.rm = TRUE))

# convert back to stars
stack_intens.1 <- st_as_stars(stack_mi60, dims = c("x", "y"))

# set the crs
st_crs(stack_intens.1) <- st_crs("+proj=longlat +datum=WGS84")

#export as tif
write_stars(stack_intens.1, paste0('./data/mrms_data/bbox_2fires/mi60_', year, '_right01.tif'))

# remove old objects
rm(stack_intens.1, stack10, stack_mi60)

```

## Merge left & right together

```{r}

# read in the left and right
right <- read_stars(paste0('./data/mrms_data/bbox_2fires/mi60_', year, '_right01.tif'))
left <- read_stars(paste0('./data/mrms_data/bbox_2fires/mi60_', year, '_left01.tif'))

# join together
mi60 <- st_mosaic(right, left)

# export as tif
write_stars(mi60, paste0('./data/mrms_data/bbox_2fires/mi60_', year, 'mi60_01.tif'))

# make df for ggplot geom_raster
mi60_df <- as.data.frame(mi60, xy = TRUE)

# put in same crs
fires <- st_transform(fires, crs = 4326)

# plot
mi60_plot <- ggplot() +
  geom_raster(data = mi60_df, 
              aes(x = x, y = y, fill = mi60_21_right01.tif)) +
  scale_fill_viridis_c(name = "MI60 (mm/hr)", 
                       option = "turbo",
                       direction = 1) +
  geom_sf(data = fires,
          fill = NA,
          color = 'black',
          lwd = 0.75) +
     theme_bw(base_size=20) +
  theme(axis.title.x = element_blank(),
    axis.title.y = element_blank())

mi60_plot

# save fig
ggsave(paste0('./data/mrms_data/bbox_2fires/mi60_20', year, '_mi60_01_plot.png'), dpi=600)

```

# Count of pixels > 10 mm/hr for MI10

- Split left and right halves
- Aggregate to 10 mins
- 10 min data (mm) to mm/hr
- Counts of MI10 above 10 mm/hr

## Left

```{r}

year <- 21

stack10 <- read_csv(paste0('./data/mrms_data/bbox_2fires/mrms20', year, '_10min_left.csv')) %>% 
  mutate(p_mmhr = p_mm*6) %>%
  select(-p_mm) %>%
  mutate(count10 = if_else(p_mmhr > 20, 1 , 0)) %>%
  select(-p_mmhr) %>%
  group_by(x,y) %>%
  summarize(sum10 = sum(count10))

# convert back to stars
stack_count10 <- st_as_stars(stack10, dims = c("x", "y"))

# set the crs
st_crs(stack_count10) <- st_crs("+proj=longlat +datum=WGS84")

#export as tif
write_stars(stack_count10, paste0('./data/mrms_data/bbox_2fires/count20_20', year, '_fil01_left.tif'))

rm(stack_count10, stack10)

beep(sound=8)

```

## Right

```{r}

stack10 <- read_csv(paste0('./data/mrms_data/bbox_2fires/mrms20', year, '_10min_right.csv')) %>% 
  mutate(p_mmhr = p_mm*6) %>%
  select(-p_mm) %>%
  mutate(count10 = if_else(p_mmhr > 20, 1 , 0)) %>%
  select(-p_mmhr) %>%
  group_by(x,y) %>%
  summarize(sum10 = sum(count10))

# convert back to stars
stack_count10 <- st_as_stars(stack10, dims = c("x", "y"))

# set the crs
st_crs(stack_count10) <- st_crs("+proj=longlat +datum=WGS84")

#export as tif
write_stars(stack_count10, paste0('./data/mrms_data/bbox_2fires/count20_20', year, '_fil01_right.tif')) 

rm(stack_count10, stack10)

beep(sound=8)

```

## Merge & plot

```{r}
# read in the left and right
right <- read_stars(paste0('./data/mrms_data/bbox_2fires/count20_20', year, '_fil01_right.tif'))
left <- read_stars(paste0('./data/mrms_data/bbox_2fires/count20_20', year, '_fil01_left.tif'))

# join together
count10 <- st_mosaic(right, left)

# export
write_stars(count10, paste0('./data/mrms_data/bbox_2fires/count_20', year, '_fil01.tif'))

# make df for ggplot
count_df <- as.data.frame(count10, xy = TRUE)

# put in same crs
fires <- st_transform(fires, crs = 4326)

#plot
count_plot <- ggplot() +
  geom_raster(data = count_df, 
              aes(x = x, y = y, fill = count20_2021_fil01_right.tif)) +
  scale_fill_viridis_c(name = "Count > 20 mm/hr", 
                       option = "turbo",
                       direction = 1) +
  geom_sf(data = fires,
          fill = NA,
          color = 'black',
          lwd = 0.75) +
     theme_bw(base_size=20) +
  theme(axis.title.x = element_blank(),
    axis.title.y = element_blank())

count_plot

# save fig
ggsave(paste0('./data/mrms_data/bbox_2fires/count20_20', year, '_fil01_plot.png'), dpi=600)

```

# P total above 10 mm/hr
P total when above 10 mm/hr

## Left

```{r}

stack10 <- read_csv(paste0('./data/mrms_data/bbox_2fires/mrms20', year, '_10min_left.csv')) %>% 
  mutate(p_mmhr = p_mm*6) %>%
  mutate(p_10 = if_else(p_mmhr > 20, p_mm, 0)) %>%
  group_by(x,y) %>%
  summarize(p10_sum = sum(p_10))

# convert back to stars
stack_p10 <- st_as_stars(stack10, dims = c("x", "y"))

# set the crs
st_crs(stack_p10) <- st_crs("+proj=longlat +datum=WGS84")

mapview(stack_p10)

#export as tif
write_stars(stack_p10, paste0('./data/mrms_data/bbox_2fires/p20_20', year, '_fil01_left.tif'))
rm(stack_p10, stack10)

#beep(sound=8)

```

## Right

```{r}

stack10 <- read_csv(paste0('./data/mrms_data/bbox_2fires/mrms20', year, '_10min_right.csv')) %>% 
  mutate(p_mmhr = p_mm*6) %>%
  mutate(p_10 = if_else(p_mmhr > 20, p_mm, 0)) %>%
  group_by(x,y) %>%
  summarize(p10_sum = sum(p_10))

# convert back to stars
stack_p10 <- st_as_stars(stack10, dims = c("x", "y"))

# set the crs
st_crs(stack_p10) <- st_crs("+proj=longlat +datum=WGS84")

mapview(stack_p10)

#export as tif
write_stars(stack_p10, paste0('./data/mrms_data/bbox_2fires/p20_20', year, '_fil01_right.tif'))
rm(stack_p10, stack10)

beep(sound=8)

```

## Merge & plot

```{r}
# read in the left and right
right <- read_stars(paste0('./data/mrms_data/bbox_2fires/p20_20', year, '_fil01_right.tif'))
left <- read_stars(paste0('./data/mrms_data/bbox_2fires/p20_20', year, '_fil01_left.tif'))

# join together
p10 <- st_mosaic(right, left)

# export
write_stars(p10, paste0('./data/mrms_data/bbox_2fires/p20_20', year, '_fil01.tif'))

# make df for ggplot
p_df <- as.data.frame(p10, xy = TRUE)

# put in same crs
fires <- st_transform(fires, crs = 4326)

#plot
p10_plot <- ggplot() +
  geom_raster(data = p_df, 
              aes(x = x, y = y, fill = p20_2021_fil01_right.tif)) +
  scale_fill_viridis_c(name = "P total > 20 mm/hr", 
                       option = "turbo",
                       direction = 1) +
  geom_sf(data = fires,
          fill = NA,
          color = 'black',
          lwd = 0.75) +
     theme_bw(base_size=20) +
  theme(axis.title.x = element_blank(),
    axis.title.y = element_blank())

p10_plot

# save fig
ggsave(paste0('./data/mrms_data/bbox_2fires/p20_20', year, '_fil01_plot.png'), dpi=600)

```

# Figure 1

* Need to make into one figure

## MRMS summer totals

```{r}

year <- 23 # **UPDATE HERE**

# load(paste0('./data/mrms_data/bbox_2fires/stack_20', year, '_fil01.Rdata'))
# 
# stack <- stack2023_fil.1 # **UPDATE HERE**
# 
# rm(list=setdiff(ls(), "stack"))
# 
# # set crs
# st_crs(stack) <- "+proj=longlat +datum=WGS84"
# 
# # sum summer 
# sum_all <- st_apply(
#   stack,
#   MARGIN = c("x", "y"),
#   FUN = sum
# )
# 
# write_stars(sum_all, paste0('./data/mrms_data/bbox_2fires/summertotal_20', year,'_fil01.tif'))

sum_all21 <- read_stars('./data/mrms_data/bbox_2fires/summertotal_2021_fil01.tif')
sum_all22 <- read_stars('./data/mrms_data/bbox_2fires/summertotal_2022_fil01.tif')
sum_all23 <- read_stars('./data/mrms_data/bbox_2fires/summertotal_2023_fil01.tif')


# make df for ggplot
p_df21<- as.data.frame(sum_all21, xy = TRUE) %>%
  rename(sum = summertotal_2021_fil01.tif) %>%
  mutate(year = 2021,
         source = 'MRMS')

p_df22<- as.data.frame(sum_all22, xy = TRUE) %>% 
  rename(sum = summertotal_2022_fil01.tif) %>%
  mutate(year = 2022,
         source = 'MRMS')
  
p_df23<- as.data.frame(sum_all23, xy = TRUE) %>%
  rename(sum = summertotal_2023_fil01.tif) %>%
  mutate(year = 2023,
         source = 'MRMS')


p_df <- bind_rows(p_df21, p_df22, p_df23)

# put in same crs
fires <- st_transform(fires, crs = 4326)

#plot
ptot_plot <- ggplot() +
  geom_raster(data = p_df, 
              aes(x = x, y = y, fill = sum)) +
  scale_fill_viridis_c(name = "P total (mm)", 
                       option = "turbo",
                       direction = 1,
                       limits = c(0, 610)) +
  facet_wrap(~as.character(year), ncol = 1) +
  geom_sf(data = fires,
          fill = NA,
          color = 'black',
          lwd = 1) +
     theme_bw(base_size=20) +
  theme(axis.title.x = element_blank(),
    axis.title.y = element_blank())

ptot_plot

# save fig
ggsave('./data/mrms_data/bbox_2fires/ptot_mrms_fil01_plot.png', dpi=600, width=15, height = 20)

```

## Gridmet summer totals

```{r}

gridmet21 <- read_stars('./data/mrms_data/bbox_2fires/2021_gridmet_summerp.tif') %>%
  st_warp(., sum_all23) %>%
  as.data.frame(., xy = TRUE) %>%
  rename(sum = 3) %>%
  mutate(year = 2021,
         source = 'Gridmet')
  
  #mapview(gridmet21) + mapview(sum_all23)

gridmet22 <- read_stars('./data/mrms_data/bbox_2fires/2022_gridmet_summerp.tif') %>%
  st_warp(., sum_all23) %>%
  as.data.frame(., xy = TRUE) %>%
  rename(sum = 3) %>%
  mutate(year = 2022,
         source = 'Gridmet')

          
gridmet23 <- read_stars('./data/mrms_data/bbox_2fires/2023_gridmet_summerp.tif') %>%
  st_warp(., sum_all23) %>%
  as.data.frame(., xy = TRUE) %>%
  rename(sum = 3) %>%
  mutate(year = 2023,
         source = 'Gridmet')


gridmet_all <- bind_rows(gridmet21, gridmet22, gridmet23)

#p_combine <- bind_rows(p_df, gridmet_all)

gridmet_all <- ggplot() +
  geom_raster(data = gridmet_all, 
              aes(x = x, y = y, fill = sum)) +
  scale_fill_viridis_c(name = "P total (mm)", 
                       option = "turbo",
                       direction = 1,
                       limits = c(0, 610)) +
  facet_wrap(~as.character(year), ncol = 1) +
  geom_sf(data = fires,
          fill = NA,
          color = 'black',
          lwd = 1) +
     theme_bw(base_size=20) +
  theme(axis.title.x = element_blank(),
    axis.title.y = element_blank())

gridmet_all

# save fig
ggsave('./data/mrms_data/bbox_2fires/ptot_gridmet_plot.png', dpi=600, width=15, height = 20)

```

## Mean RQI by year

```{r}

# 2023 RQI mean
load("./data/mrms_data/bbox_2fires/stack_RQI_2023.RData")

rqi_mean_2023 <- st_apply(
  stack_rqi2023,
  MARGIN = c("x", "y"),
  FUN = mean
)

rqi23 <- as.data.frame(rqi_mean_2023, xy = TRUE) %>%
  mutate(year = 2023,
         source = 'RQI')

# 2022 RQI mean
load("./data/mrms_data/bbox_2fires/stack_RQI_2022.RData")

rqi_mean_2022 <- st_apply(
  stack_rqi2022,
  MARGIN = c("x", "y"),
  FUN = mean
)

rqi22 <- as.data.frame(rqi_mean_2022, xy = TRUE) %>%
  mutate(year = 2022,
         source = 'RQI')


# 2021 RQI mean
load("./data/mrms_data/bbox_2fires/stack_RQI_2021.RData")

rqi_mean_2021 <- st_apply(
  stack_rqi2021,
  MARGIN = c("x", "y"),
  FUN = mean
)

rqi21 <- as.data.frame(rqi_mean_2021, xy = TRUE) %>%
  mutate(year = 2021,
         source = 'RQI')

rqi <- bind_rows(rqi21, rqi22, rqi23)

# figure
rqi_all <- ggplot() +
  geom_raster(data = rqi, 
              aes(x = x, y = y, fill = mean)) +
  scale_fill_viridis_c(name = "Mean RQI", 
                       option = "cividis",
                       direction = 1) +
  facet_wrap(~as.character(year), ncol = 1) +
  geom_sf(data = fires,
          fill = NA,
          color = 'black',
          lwd = 1) +
     theme_bw(base_size=20) +
  theme(axis.title.x = element_blank(),
    axis.title.y = element_blank())

rqi_all

# save fig
ggsave('./data/mrms_data/bbox_2fires/rqi_mean_plot.png', dpi=600, width=15, height = 20)

```

# Monthly sums

```{r}

load('./bbox_2fires/stack_2023_fil1.Rdata')

# set crs
st_crs(stack2023_fil1) <- "+proj=longlat +datum=WGS84"

# june 2023 sum
june_stack <- stack2023_fil1 %>%
  filter(datetime > ymd_hms('2023-06-01 00:00:00'),
         datetime < ymd_hms('2023-07-01 00:00:00'))

june_sum_23 <- st_apply(
  june_stack,
  MARGIN = c("x", "y"),
  FUN = sum
)

write_stars(june_sum_23, './bbox_2fires/june_sum_23_fil1.tif')

mapview(june_sum_23) + 
  mapview(fires, col.regions = NA, col = "black", alpha.regions = 0)

# july 2023 sum
july_stack <- stack2023_fil1 %>%
  filter(datetime > ymd_hms('2023-07-01 00:00:00'),
         datetime < ymd_hms('2023-08-01 00:00:00'))

july_sum_23 <- st_apply(
  july_stack,
  MARGIN = c("x", "y"),
  FUN = sum
)

write_stars(july_sum_23, './bbox_2fires/july_sum_23_fil1.tif')

mapview(july_sum_23) + 
  mapview(fires, col.regions = NA, col = "black", alpha.regions = 0)

# august 2023 sum
aug_stack <- stack2023_fil1 %>%
  filter(datetime > ymd_hms('2023-08-01 00:00:00'),
         datetime < ymd_hms('2023-09-01 00:00:00'))

aug_sum_23 <- st_apply(
  aug_stack,
  MARGIN = c("x", "y"),
  FUN = sum
)

write_stars(aug_sum_23, './bbox_2fires/aug_sum_23_fil1.tif')

mapview(aug_sum_23) + 
  mapview(fires, col.regions = NA, col = "black", alpha.regions = 0)

# september 2023 sum
sept_stack <- stack2023_fil1 %>%
  filter(datetime > ymd_hms('2023-09-01 00:00:00'),
         datetime < ymd_hms('2023-10-01 00:00:00'))

sept_sum_23 <- st_apply(
  sept_stack,
  MARGIN = c("x", "y"),
  FUN = sum
)

write_stars(sept_sum_23, './bbox_2fires/sept_sum_23_fil1.tif')

mapview(sept_sum_23) + 
  mapview(fires, col.regions = NA, col = "black", alpha.regions = 0)


june_tibble <- as_tibble(june_sum_23) %>%
  mutate(month = 'June', year = '2023')

july_tibble <- as_tibble(july_sum_23) %>%
  mutate(month = 'July', year = '2023')

aug_tibble <- as_tibble(aug_sum_23) %>%
  mutate(month = 'August', year = '2023')

sept_tibble <- as_tibble(sept_sum_23) %>%
  mutate(month = 'September', year = '2023')

mo_sums23 <- bind_rows(june_tibble, july_tibble,
                     aug_tibble, sept_tibble) %>%
  mutate(month = as.factor(month))

# test
mo_sums_plot <- ggplot() +
  geom_raster(data = mo_sums23, 
              aes(x = x, y = y, fill = sum)) +
  scale_fill_viridis_c(name = "Monthly sums (mm)", 
                       option = "turbo",
                       direction = 1) +
  facet_wrap(~month) +
  geom_sf(data = fires,
          fill = NA,
          color = 'black',
          lwd = 0.75) +
     theme_bw(base_size=20) +
  theme(axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    legend.text = element_text(size = 10),
    legend.title = element_text(size = 12),
    legend.box.margin = margin(t = -10, r = -15, b = -10, l = -15))

mo_sums_plot

ggsave('./bbox_2fires/mo_sums_23_fil1_plot.png', dpi=600)

mo_sum_all <- bind_rows(mo_sums21, mo_sums22, mo_sums23)

# all years and months plot
mo_sums_plot <- ggplot() +
  geom_raster(data = mo_sum_all, 
              aes(x = x, y = y, fill = sum)) +
  scale_fill_viridis_c(name = "Monthly sums (mm)", 
                       option = "turbo",
                       direction = 1) +
     theme_bw(base_size=20) +
  facet_grid(rows = vars(year), cols = vars(month)) +
    # geom_sf(data = fires,
    #       fill = NA,
    #       color = 'black',
    #       lwd = 0.75) +
  theme(axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    legend.text = element_text(size = 10),
    legend.title = element_text(size = 12),
    legend.box.margin = margin(t = -10, r = -15, b = -10, l = -15))

mo_sums_plot

ggsave('./bbox_2fires/mo_sums_all_fil1_plot.png', dpi=600)

```

# Figure 2

## P total above MI60 10 mm/hr

### Get MI60

```{r}
year <- 23
pover <- 10

stack10left <- read_csv(paste0('./data/mrms_data/bbox_2fires/mrms20', year, '_10min_left.csv')) %>% 
  group_by(x,y) %>%
  # mutate(id = cur_group_id()) %>%
  # filter(id == 6621) %>%
  arrange(datetime_round) %>% 
  #mutate(sum_mm = (rollapplyr(p_mm, width = 3, FUN = sum, partial = T))*2) %>% 
  mutate(sum_mm = p_mm*6) %>% 
  mutate(over = if_else(sum_mm > pover, p_mm, 0)) %>%
  summarize(p_over = sum(over))

stack10right <- read_csv(paste0('./data/mrms_data/bbox_2fires/mrms20', year, '_10min_right.csv')) %>% 
  group_by(x,y) %>%
  arrange(datetime_round) %>% 
  #mutate(sum_mm = (rollapplyr(p_mm, width = 3, FUN = sum, partial = T))*2) %>% 
  mutate(sum_mm = p_mm*6) %>% 
  mutate(over = if_else(sum_mm > pover, p_mm, 0)) %>%
  summarize(p_over = sum(over))

mi30_p_23 <- bind_rows(stack10left, stack10right) %>%
  mutate(year = 2023)

year <- 22

stack10left <- read_csv(paste0('./data/mrms_data/bbox_2fires/mrms20', year, '_10min_left.csv')) %>% 
  group_by(x,y) %>%
  arrange(datetime_round) %>% 
  #mutate(sum_mm = (rollapplyr(p_mm, width = 3, FUN = sum, partial = T))*2) %>% 
  mutate(sum_mm = p_mm*6) %>% 
  mutate(over = if_else(sum_mm > pover, p_mm, 0)) %>%
  summarize(p_over = sum(over))

stack10right <- read_csv(paste0('./data/mrms_data/bbox_2fires/mrms20', year, '_10min_right.csv')) %>% 
  group_by(x,y) %>%
  arrange(datetime_round) %>% 
  #mutate(sum_mm = (rollapplyr(p_mm, width = 3, FUN = sum, partial = T))*2) %>% 
  mutate(sum_mm = p_mm*6) %>% 
  mutate(over = if_else(sum_mm > pover, p_mm, 0)) %>%
  summarize(p_over = sum(over))

mi30_p_22 <- bind_rows(stack10left, stack10right) %>%
  mutate(year = 2022)

year <- 21

stack10left <- read_csv(paste0('./data/mrms_data/bbox_2fires/mrms20', year, '_10min_left.csv')) %>% 
  group_by(x,y) %>%
  arrange(datetime_round) %>% 
  #mutate(sum_mm = (rollapplyr(p_mm, width = 3, FUN = sum, partial = T))*2) %>% 
  mutate(sum_mm = p_mm*6) %>% 
  mutate(over = if_else(sum_mm > pover, p_mm, 0)) %>%
  summarize(p_over = sum(over))

stack10right <- read_csv(paste0('./data/mrms_data/bbox_2fires/mrms20', year, '_10min_right.csv')) %>% 
  group_by(x,y) %>%
  arrange(datetime_round) %>% 
  #mutate(sum_mm = (rollapplyr(p_mm, width = 3, FUN = sum, partial = T))*2) %>% 
  mutate(sum_mm = p_mm*6) %>% 
  mutate(over = if_else(sum_mm > pover, p_mm, 0)) %>%
  summarize(p_over = sum(over))

mi30_p_21 <- bind_rows(stack10left, stack10right) %>%
  mutate(year = 2021)

mi30_p <- bind_rows(mi30_p_23, mi30_p_22, mi30_p_21)

# plot
p_mi30_plot <- ggplot() +
  geom_raster(data = mi30_p, 
              aes(x = x, y = y, fill = p_over)) +
  facet_wrap(~year, ncol=1) +
  scale_fill_viridis_c(name = "P total > MI10 10 mm/hr", 
                       option = "turbo",
                       direction = 1) +
  geom_sf(data = fires,
          fill = NA,
          color = 'black',
          lwd = 0.75) +
     theme_bw(base_size=20) +
  theme(axis.title.x = element_blank(),
    axis.title.y = element_blank())

p_mi30_plot

# save fig
ggsave('./data/mrms_data/bbox_2fires/pover10_mi10_fil01_plot.png', dpi=600, width=15, height = 20)

```



### Merge & plot

```{r}
# read in the left and right
right <- read_stars(paste0('./data/mrms_data/bbox_2fires/p20_20', year, '_fil01_right.tif'))
left <- read_stars(paste0('./data/mrms_data/bbox_2fires/p20_20', year, '_fil01_left.tif'))

# join together
p10 <- st_mosaic(right, left)

# export
write_stars(p10, paste0('./data/mrms_data/bbox_2fires/p20_20', year, '_fil01.tif'))

# make df for ggplot
p_df <- as.data.frame(p10, xy = TRUE)

# put in same crs
fires <- st_transform(fires, crs = 4326)

#plot
p10_plot <- ggplot() +
  geom_raster(data = p_df, 
              aes(x = x, y = y, fill = p20_2021_fil01_right.tif)) +
  scale_fill_viridis_c(name = "P total > 20 mm/hr", 
                       option = "turbo",
                       direction = 1) +
  geom_sf(data = fires,
          fill = NA,
          color = 'black',
          lwd = 0.75) +
     theme_bw(base_size=20) +
  theme(axis.title.x = element_blank(),
    axis.title.y = element_blank())

p10_plot

# save fig
ggsave(paste0('./data/mrms_data/bbox_2fires/p20_20', year, '_fil01_plot.png'), dpi=600)

```


