---
title: "mrms spatial"
author: "Megan Sears"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(
  echo = F,
  message = F, 
  warning  = F)

# load packages
library(here)
library(tidyverse)
library(lubridate)
library(zoo)
library(terra)
library(stars)
library(tmap)
library(sf)
library(mapview)
library(zoo)
library(ggspatial)
library(beepr)
library(future.apply)
library(future)

```

# Load data and create raster stack by year

```{r}
# read in fire boundaries
et <- st_read("./data/GIS/burn_boundaries/co4020310623920201014_20200904_20210907_burn_bndy.shp")
cp <- st_read('./data/GIS/burn_boundaries/co4060910587920200813_20180915_20210907_burn_bndy.shp')

#
fires <- rbind(et, cp)
#
# fires_stars <- st_as_stars(fires)
# 
# # List all the files in the directory
# filenames <- list.files("/Users/megansears/Documents/MRMS/bbox_2fires/2min_2021", pattern = ".tif", full.names = TRUE)
# 
# datetime <- list.files("/Users/megansears/Documents/MRMS/bbox_2fires/2min_2021", pattern = ".tif", full.names = F)
# 
# timestamps <- substr(datetime, 12, 26)
# datetime_seq <- ymd_hms(timestamps) - (7 * 60 * 60)
# 
# # Read all raster files and stack them together
# stack <- read_stars(filenames, along = 3)
# 
# # Set the datetime dimension of the stack
# stack_date <- st_set_dimensions(stack, 3, values = datetime_seq, names = "datetime")
# 
# # Filter the stack_date object by datetime
# stack2021 <- stack_date %>%
#   setNames('MI2_mmhr') %>%
#   mutate(p_mm =  MI2_mmhr*(1/30)) %>%
#   dplyr::select(-MI2_mmhr) %>%
#   filter(datetime > ymd_hms('2021-05-31 23:58:00'),
#          datetime < ymd_hms('2021-09-30 23:58:00'))
# 
# rm(stack, stack_date)
# 
# #save.image("/Users/megansears/Documents/Repos/post-fire_rainfall/bbox_2fires/stack_2023.RData")
# #save.image("/Users/megansears/Documents/Repos/post-fire_rainfall/bbox_2fires/stack_2022.RData")
# #save.image("/Users/megansears/Documents/Repos/post-fire_rainfall/bbox_2fires/stack_2021.RData")

```

# Filter out <1 mm

```{r}
# 
# new_crs <- st_crs(4326)
# 
# fires <- st_transform(fires, crs = new_crs)
# 
# # first filter a smaller area so I can work with it easier
# stack23_crop <- st_crop(stack2023, cp)

# filter less than 1
filter_function <- function(x) {
  x[x < 0.254] <- 0
  return(x)
}

# Load your data
load('/Users/megansears/Documents/Repos/post-fire_rainfall/bbox_2fires/stack_2023.RData')

# Set up parallel backend
plan(multisession, workers = 6)

# Use st_apply with future.apply for parallel processing
stack2023_fil254 <- st_apply(
  stack2023,
  MARGIN = c("x", "y", "datetime"),
  FUN = function(x) future_lapply(x, filter_function)
)

# Beep when done
beep(sound=8)

# Clean up
rm(stack2023)
plan(sequential)  # Reset the plan to sequential after processing
beep(sound=8)
rm(stack2023)

save.image("/Users/megansears/Documents/Repos/post-fire_rainfall/bbox_2fires/stack_2023_fil254.RData")
rm(list = ls())

# now do 2022
load("/Users/megansears/Documents/Repos/post-fire_rainfall/bbox_2fires/stack_2022.RData")

# filter out values less than 1 mm
stack2022_fil254 <- st_apply(
  stack2022,
  MARGIN = c("x", "y", "datetime"),  # dimensions
  FUN = filter_function
)
rm(stack2022)

save.image("/Users/megansears/Documents/Repos/post-fire_rainfall/bbox_2fires/stack_2022_fil254.RData")
rm(list = ls())

# 2021
load("/Users/megansears/Documents/Repos/post-fire_rainfall/bbox_2fires/stack_2021.RData")

# filter out values less than 1 mm 
stack2021_fil254 <- st_apply(
  stack2021,
  MARGIN = c("x", "y", "datetime"),  # dimensions
  FUN = filter_function
)
rm(stack2021)

save.image("/Users/megansears/Documents/Repos/post-fire_rainfall/bbox_2fires/stack_2021_fil254.RData")

```

# MI60

The stack (or tibble) is too large, exhausts memory. The raster stacks need to be cut in half down the middle.

## Left half first

```{r}
#load in stack
load('./bbox_2fires/stack_2021_fil1.Rdata')

# set crs
st_crs(stack2021_fil1) <- "+proj=longlat +datum=WGS84"

# bbox of the whole area
bbox <- st_bbox(stack2021_fil1)

# Extract bbox coords
xmin <- bbox['xmin']
xmax <- bbox['xmax']
ymin <- bbox['ymin']
ymax <- bbox['ymax']

# Calculate mid_x
mid_x <- as.numeric(xmin + (xmax - xmin) / 2)

# bbox left site
left_bbox <- st_bbox(c(xmin = as.numeric(xmin), 
                       xmax = mid_x, 
                       ymin = as.numeric(ymin), 
                       ymax = as.numeric(ymax)), 
                     crs = st_crs(4326))

# Crop the left half
left_half <- st_crop(stack2021_fil1, y = left_bbox) 

rm(stack2021_fil1)

# make df
tibble <- as_tibble(left_half)
rm(left_half)
gc()

# aggregate to 10 min
stack10 <- tibble %>%
  mutate(datetime_round = ceiling_date(datetime, "10 mins")) %>%
  group_by(x, y, datetime_round) %>%
  rename(p_mm = filter_function) %>%
  summarize(p_mm = sum(p_mm)) %>%
  drop_na(p_mm)

# calculates max MI60 over a summer
compute_MI60 <- function(df) {
  # Calculate the rolling sum over 6 intervals (60 minutes)
  rolling_sums <- rollapply(df, width = 6, FUN = sum, na.rm = TRUE, fill = NA, align = "right")
  # Find the max of rolling sums
  max(rolling_sums, na.rm = TRUE)
}

# Calculate MI60 for each pixel over the 10-min data
stack_mi60 <- stack10 %>%
  group_by(x, y) %>%
  arrange(datetime_round) %>%
  mutate(MI60 = compute_MI60(p_mm)) %>%
  summarize(maxMI60 = max(MI60, na.rm = TRUE))

# convert back to stars
stack_intens1 <- st_as_stars(stack_mi60, dims = c("x", "y"))

# set the crs
st_crs(stack_intens1) <- st_crs("+proj=longlat +datum=WGS84")

# export as tif
write_stars(stack_intens1, './bbox_2fires/mi60_21_left1.tif')

# remove old objects
rm(stack_intens1, stack10, tibble, stack_mi60)

```

## Right half

```{r}
#load in stack
load('./bbox_2fires/stack_2021_fil1.Rdata')

# set crs
st_crs(stack2021_fil1) <- "+proj=longlat +datum=WGS84"

# bbox RIGHT site
right_bbox <- st_bbox(c(xmin = mid_x, 
                       xmax = as.numeric(xmax), 
                       ymin = as.numeric(ymin), 
                       ymax = as.numeric(ymax)), 
                     crs = st_crs(4326))

# Crop the right half
right_half <- st_crop(stack2021_fil1, y = right_bbox)

rm(stack2021_fil1)

# make df
tibble <- as_tibble(right_half)
rm(right_half)
gc()

# aggregate to 10 min
stack10 <- tibble %>%
  mutate(datetime_round = ceiling_date(datetime, "10 mins")) %>%
  group_by(x, y, datetime_round) %>%
  rename(p_mm = filter_function) %>%
  summarize(p_mm = sum(p_mm)) %>%
  drop_na(p_mm)

# Calculate MI60 for each pixel over 10-min timesteps
stack_mi60 <- stack10 %>%
  group_by(x, y) %>%
  arrange(datetime_round) %>%
  mutate(MI60 = compute_MI60(p_mm)) %>%
  summarize(maxMI60 = max(MI60, na.rm = TRUE))

# convert back to stars
stack_intens1 <- st_as_stars(stack_mi60, dims = c("x", "y"))

# set the crs
st_crs(stack_intens1) <- st_crs("+proj=longlat +datum=WGS84")

#export as tif
write_stars(stack_intens1, './bbox_2fires/mi60_21_right1.tif')

# remove old objects
rm(stack_intens1, stack10, tibble, stack_mi60)

```

## Merge left & right together

```{r}

# read in the left and right
right <- read_stars('./bbox_2fires/mi60_21_right1.tif')
left <- read_stars('./bbox_2fires/mi60_21_left1.tif')

# join together
mi60_21 <- st_mosaic(right, left)

# export as tif
write_stars(mi60_21, './bbox_2fires/mi60_21_1.tif')

# make df for ggplot geom_raster
mi60_df <- as.data.frame(mi60_21, xy = TRUE)

# put in same crs
fires <- st_transform(fires, crs = 4326)

# plot
mi60_plot <- ggplot() +
  geom_raster(data = mi60_df, 
              aes(x = x, y = y, fill = mi60_21_right1.tif)) +
  scale_fill_viridis_c(name = "MI60 (mm/hr)", 
                       option = "turbo",
                       direction = 1) +
  geom_sf(data = fires,
          fill = NA,
          color = 'black',
          lwd = 0.75) +
     theme_bw(base_size=20) +
  theme(axis.title.x = element_blank(),
    axis.title.y = element_blank())

mi60_plot

# save fig
ggsave('./bbox_2fires/2021_mi60_1_plot.png', dpi=600)

```

# Count of pixels > 10 mm/hr for MI10

- Split left and right halves
- Aggregate to 10 mins
- 10 min data (mm) to mm/hr
- Counts of MI10 above 10 mm/hr

## Left

```{r}

#load in stack
load('./bbox_2fires/stack_2023_fil1.Rdata')

# set crs
st_crs(stack2023_fil1) <- "+proj=longlat +datum=WGS84"

# bbox of the whole area
bbox <- st_bbox(stack2023_fil1)

# Extract bbox coords
xmin <- bbox['xmin']
xmax <- bbox['xmax']
ymin <- bbox['ymin']
ymax <- bbox['ymax']

# Calculate mid_x
mid_x <- as.numeric(xmin + (xmax - xmin) / 2)

# bbox left site
left_bbox <- st_bbox(c(xmin = as.numeric(xmin), 
                       xmax = mid_x, 
                       ymin = as.numeric(ymin), 
                       ymax = as.numeric(ymax)), 
                     crs = st_crs(4326))

# Crop the left half
left_half <- st_crop(stack2023_fil1, y = left_bbox)

rm(stack2023_fil1)

# make df
tibble <- as_tibble(left_half)
rm(left_half)
gc()

# aggregate to 10 min then get into mm/hr
# count values above 10 mm/hr for MI10
stack10 <- tibble %>%
  mutate(datetime_round = ceiling_date(datetime, "10 mins")) %>%
  group_by(x, y, datetime_round) %>%
  rename(p_mm = filter_function) %>%
  summarize(p_mm = sum(p_mm)) %>%
  drop_na(p_mm) %>% 
  mutate(p_mmhr = p_mm*6) %>%
  select(-p_mm) %>%
  mutate(count10 = if_else(p_mmhr > 10, 1 , 0)) %>%
  select(-p_mmhr) %>%
  group_by(x,y) %>%
  summarize(sum10 = sum(count10))

# convert back to stars
stack_count10 <- st_as_stars(stack10, dims = c("x", "y"))

# set the crs
st_crs(stack_count10) <- st_crs("+proj=longlat +datum=WGS84")

#export as tif
write_stars(stack_count10, './bbox_2fires/count10_2023_fil1_left.tif')

rm(stack_count10, stack10, tibble)

beep(sound=8)

```

## Right

```{r}

#load in stack
load('./bbox_2fires/stack_2023_fil1.Rdata')

# set crs
st_crs(stack2023_fil1) <- "+proj=longlat +datum=WGS84"

# bbox RIGHT site
right_bbox <- st_bbox(c(xmin = mid_x, 
                       xmax = as.numeric(xmax), 
                       ymin = as.numeric(ymin), 
                       ymax = as.numeric(ymax)), 
                     crs = st_crs(4326))

# Crop the right half
right_half <- st_crop(stack2023_fil1, y = right_bbox)

rm(stack2023_fil1)

# make df
tibble <- as_tibble(right_half)
rm(right_half)
gc()

# aggregate to 10 min then get into mm/hr
# count values above 10 mm/hr for MI10
stack10 <- tibble %>%
  mutate(datetime_round = ceiling_date(datetime, "10 mins")) %>%
  group_by(x, y, datetime_round) %>%
  rename(p_mm = filter_function) %>%
  summarize(p_mm = sum(p_mm)) %>%
  drop_na(p_mm) %>% 
  mutate(p_mmhr = p_mm*6) %>%
  select(-p_mm) %>%
  mutate(count10 = if_else(p_mmhr > 10, 1 , 0)) %>%
  select(-p_mmhr) %>%
  group_by(x,y) %>%
  summarize(sum10 = sum(count10))

# convert back to stars
stack_count10 <- st_as_stars(stack10, dims = c("x", "y"))

# set the crs
st_crs(stack_count10) <- st_crs("+proj=longlat +datum=WGS84")

#export as tif
write_stars(stack_count10, './bbox_2fires/count10_2023_fil1_right.tif')

rm(stack_count10, stack10, tibble)

beep(sound=8)

```

## Merge & plot

```{r}
# read in the left and right
right <- read_stars('./bbox_2fires/count10_2023_fil1_right.tif')
left <- read_stars('./bbox_2fires/count10_2023_fil1_left.tif')

# join together
count10_23 <- st_mosaic(right, left)

# export
write_stars(count10_23, './bbox_2fires/count_2023_fil1.tif')

# make df for ggplot
count_df <- as.data.frame(count10_23, xy = TRUE)

# put in same crs
fires <- st_transform(fires, crs = 4326)

#plot
count_plot <- ggplot() +
  geom_raster(data = count_df, 
              aes(x = x, y = y, fill = count10_2023_fil1_right.tif)) +
  scale_fill_viridis_c(name = "Count > 10 mm/hr", 
                       option = "turbo",
                       direction = 1) +
  geom_sf(data = fires,
          fill = NA,
          color = 'black',
          lwd = 0.75) +
     theme_bw(base_size=20) +
  theme(axis.title.x = element_blank(),
    axis.title.y = element_blank())

count_plot

# save fig
ggsave('./bbox_2fires/count10_2023_fil1_plot.png', dpi=600)

```

# P total above 10 mm/hr
P total when above 10 mm/hr

## Left

```{r}

#load in stack
load('./bbox_2fires/stack_2023_fil1.Rdata')

# set crs
st_crs(stack2023_fil1) <- "+proj=longlat +datum=WGS84"

# bbox of the whole area
bbox <- st_bbox(stack2023_fil1)

# Extract bbox coords
xmin <- bbox['xmin']
xmax <- bbox['xmax']
ymin <- bbox['ymin']
ymax <- bbox['ymax']

# Calculate mid_x
mid_x <- as.numeric(xmin + (xmax - xmin) / 2)

# bbox left site
left_bbox <- st_bbox(c(xmin = as.numeric(xmin), 
                       xmax = mid_x, 
                       ymin = as.numeric(ymin), 
                       ymax = as.numeric(ymax)), 
                     crs = st_crs(4326))

# Crop the left half
left_half <- st_crop(stack2023_fil1, y = left_bbox)

rm(stack2023_fil1)

# make df
tibble <- as_tibble(left_half)
rm(left_half)
gc()

# aggregate to 10 min - something is wrong here
stack10 <- tibble %>%
  mutate(datetime_round = ceiling_date(datetime, "10 mins")) %>%
  group_by(x, y, datetime_round) %>%
  rename(p_mm = filter_function) %>%
  summarize(p_mm = sum(p_mm)) %>%
  drop_na(p_mm) %>% 
  mutate(p_mmhr = p_mm*6) %>%
  mutate(p_10 = if_else(p_mmhr > 10, p_mm, 0)) #%>%
  group_by(x,y) %>%
  summarize(p10_sum = sum(p_10))

# testing - delete later
test <- stack10 %>%
  slice(5000:6000)
  
# convert back to stars
stack_p10 <- st_as_stars(stack10, dims = c("x", "y"))

# set the crs
st_crs(stack_p10) <- st_crs("+proj=longlat +datum=WGS84")

#export as tif
write_stars(stack_p10, './bbox_2fires/p10_2023_fil1_left.tif')
rm(stack_p10, stack10, tibble)

#beep(sound=8)

```

## Right

```{r}

#load in stack
load('./bbox_2fires/stack_2023_fil1.Rdata')

# set crs
st_crs(stack2023_fil1) <- "+proj=longlat +datum=WGS84"

# bbox RIGHT site
right_bbox <- st_bbox(c(xmin = mid_x, 
                       xmax = as.numeric(xmax), 
                       ymin = as.numeric(ymin), 
                       ymax = as.numeric(ymax)), 
                     crs = st_crs(4326))

# Crop the left half
right_half <- st_crop(stack2023_fil1, y = right_bbox)

rm(stack2023_fil1)

# make df
tibble <- as_tibble(right_half)
rm(right_half)
gc()

# aggregate to 10 min
stack10 <- tibble %>%
  mutate(datetime_round = ceiling_date(datetime, "10 mins")) %>%
  group_by(x, y, datetime_round) %>%
  rename(p_mm = filter_function) %>%
  summarize(p_mm = sum(p_mm)) %>%
  drop_na(p_mm) %>% 
  mutate(p_mmhr = p_mm*6) %>%
  mutate(p_10 = if_else(p_mmhr > 10, p_mm, 0)) %>%
  group_by(x,y) %>%
  summarize(p10_sum = sum(p_10))

# convert back to stars
stack_p10 <- st_as_stars(stack10, dims = c("x", "y"))

# set the crs
st_crs(stack_p10) <- st_crs("+proj=longlat +datum=WGS84")

#export as tif
write_stars(stack_p10, './bbox_2fires/p10_2023_fil1_right.tif')
rm(stack_p10, stack10, tibble)

beep(sound=8)

```

## Merge & plot

```{r}
# read in the left and right
right <- read_stars('./bbox_2fires/p10_2023_fil1_right.tif')
left <- read_stars('./bbox_2fires/p10_2023_fil1_left.tif')

# join together
p10_23 <- st_mosaic(right, left)

# export
write_stars(p10_23, './bbox_2fires/p10_2023_fil1.tif')

# make df for ggplot
p_df <- as.data.frame(p10_23, xy = TRUE)

# put in same crs
fires <- st_transform(fires, crs = 4326)

#plot
p10_plot <- ggplot() +
  geom_raster(data = p_df, 
              aes(x = x, y = y, fill = p10_2023_fil1_right.tif)) +
  scale_fill_viridis_c(name = "P total > 10 mm/hr", 
                       option = "turbo",
                       direction = 1) +
  geom_sf(data = fires,
          fill = NA,
          color = 'black',
          lwd = 0.75) +
     theme_bw(base_size=20) +
  theme(axis.title.x = element_blank(),
    axis.title.y = element_blank())

p10_plot

# save fig
ggsave('./bbox_2fires/p10_2023_fil1_plot.png', dpi=600)

```

# Summer totals

```{r}

#load in stack
load('./bbox_2fires/stack_2021_fil1.Rdata')

# set crs
st_crs(stack2021_fil1) <- "+proj=longlat +datum=WGS84"

# sum summer 2021
sum_all2021 <- st_apply(
  stack2021_fil1,
  MARGIN = c("x", "y"),
  FUN = sum
)

write_stars(sum_all2023, './bbox_2fires/summertotal_2023_fil1.tif')

# make df for ggplot
p_df <- as.data.frame(sum_all2021, xy = TRUE)

# put in same crs
fires <- st_transform(fires, crs = 4326)

#plot
ptot_plot <- ggplot() +
  geom_raster(data = p_df, 
              aes(x = x, y = y, fill = sum)) +
  scale_fill_viridis_c(name = "P total (mm)", 
                       option = "turbo",
                       direction = 1) +
  geom_sf(data = fires,
          fill = NA,
          color = 'black',
          lwd = 1) +
     theme_bw(base_size=20) +
  theme(axis.title.x = element_blank(),
    axis.title.y = element_blank())

ptot_plot

# save fig
ggsave('./bbox_2fires/ptot_2021_fil1_plot.png', dpi=600)



# mapview(sum_all2021) + 
#   mapview(fires, col.regions = NA, col = "black", alpha.regions = 0)
# 
# library(raster)
# 
# r <- as(sum_all2023, "Raster")
# r_df <- as.data.frame(r, xy = TRUE)
# colnames(r_df) <- c("x", "y", "value")
# 
# fire_poly <- as(fires_stars, 'Spatial')
# fire_poly <- spTransform(fire_poly, CRS("+proj=longlat +datum=WGS84"))
# fire_poly <- fire_poly[-2, ]
# fire_poly <- fire_poly[-1, ]
# 
# fire_poly_et <- as(fires_stars, 'Spatial')
# fire_poly_et <- spTransform(fire_poly_et, CRS("+proj=longlat +datum=WGS84"))
# fire_poly_et <- fire_poly_et[-3, ]
# fire_poly_et <- fire_poly_et[-2, ]
# plot(fire_poly_et)
# 
# p2023 <- ggplot(r_df, aes(x = x, y = y, fill = value)) +
#   geom_raster() +
#   geom_polygon(data=fire_poly, aes(x =long, y = lat), fill = "transparent", color = "black") +
#   geom_polygon(data=fire_poly_et, aes(x =long, y = lat), fill = "transparent", color = "black") +
#   scale_fill_viridis_b() +
#     theme_bw() +
#   theme(
#     axis.title.x = element_blank(),
#     axis.title.y = element_blank())
# 
# p2023
# 
# ggsave("2023_total.png", plot = p2023, width = 6, height = 4, dpi = 800)

```

# Monthly sums

```{r}

load('./bbox_2fires/stack_2023_fil1.Rdata')

# set crs
st_crs(stack2023_fil1) <- "+proj=longlat +datum=WGS84"

# june 2023 sum
june_stack <- stack2023_fil1 %>%
  filter(datetime > ymd_hms('2023-06-01 00:00:00'),
         datetime < ymd_hms('2023-07-01 00:00:00'))

june_sum_23 <- st_apply(
  june_stack,
  MARGIN = c("x", "y"),
  FUN = sum
)

write_stars(june_sum_23, './bbox_2fires/june_sum_23_fil1.tif')

mapview(june_sum_23) + 
  mapview(fires, col.regions = NA, col = "black", alpha.regions = 0)

# july 2023 sum
july_stack <- stack2023_fil1 %>%
  filter(datetime > ymd_hms('2023-07-01 00:00:00'),
         datetime < ymd_hms('2023-08-01 00:00:00'))

july_sum_23 <- st_apply(
  july_stack,
  MARGIN = c("x", "y"),
  FUN = sum
)

write_stars(july_sum_23, './bbox_2fires/july_sum_23_fil1.tif')

mapview(july_sum_23) + 
  mapview(fires, col.regions = NA, col = "black", alpha.regions = 0)

# august 2023 sum
aug_stack <- stack2023_fil1 %>%
  filter(datetime > ymd_hms('2023-08-01 00:00:00'),
         datetime < ymd_hms('2023-09-01 00:00:00'))

aug_sum_23 <- st_apply(
  aug_stack,
  MARGIN = c("x", "y"),
  FUN = sum
)

write_stars(aug_sum_23, './bbox_2fires/aug_sum_23_fil1.tif')

mapview(aug_sum_23) + 
  mapview(fires, col.regions = NA, col = "black", alpha.regions = 0)

# september 2023 sum
sept_stack <- stack2023_fil1 %>%
  filter(datetime > ymd_hms('2023-09-01 00:00:00'),
         datetime < ymd_hms('2023-10-01 00:00:00'))

sept_sum_23 <- st_apply(
  sept_stack,
  MARGIN = c("x", "y"),
  FUN = sum
)

write_stars(sept_sum_23, './bbox_2fires/sept_sum_23_fil1.tif')

mapview(sept_sum_23) + 
  mapview(fires, col.regions = NA, col = "black", alpha.regions = 0)


june_tibble <- as_tibble(june_sum_23) %>%
  mutate(month = 'June', year = '2023')

july_tibble <- as_tibble(july_sum_23) %>%
  mutate(month = 'July', year = '2023')

aug_tibble <- as_tibble(aug_sum_23) %>%
  mutate(month = 'August', year = '2023')

sept_tibble <- as_tibble(sept_sum_23) %>%
  mutate(month = 'September', year = '2023')

mo_sums23 <- bind_rows(june_tibble, july_tibble,
                     aug_tibble, sept_tibble) %>%
  mutate(month = as.factor(month))

# test
mo_sums_plot <- ggplot() +
  geom_raster(data = mo_sums23, 
              aes(x = x, y = y, fill = sum)) +
  scale_fill_viridis_c(name = "Monthly sums (mm)", 
                       option = "turbo",
                       direction = 1) +
  facet_wrap(~month) +
  geom_sf(data = fires,
          fill = NA,
          color = 'black',
          lwd = 0.75) +
     theme_bw(base_size=20) +
  theme(axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    legend.text = element_text(size = 10),
    legend.title = element_text(size = 12),
    legend.box.margin = margin(t = -10, r = -15, b = -10, l = -15))

mo_sums_plot

ggsave('./bbox_2fires/mo_sums_23_fil1_plot.png', dpi=600)

mo_sum_all <- bind_rows(mo_sums21, mo_sums22, mo_sums23)

# all years and months plot
mo_sums_plot <- ggplot() +
  geom_raster(data = mo_sum_all, 
              aes(x = x, y = y, fill = sum)) +
  scale_fill_viridis_c(name = "Monthly sums (mm)", 
                       option = "turbo",
                       direction = 1) +
     theme_bw(base_size=20) +
  facet_grid(rows = vars(year), cols = vars(month)) +
    # geom_sf(data = fires,
    #       fill = NA,
    #       color = 'black',
    #       lwd = 0.75) +
  theme(axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    legend.text = element_text(size = 10),
    legend.title = element_text(size = 12),
    legend.box.margin = margin(t = -10, r = -15, b = -10, l = -15))

mo_sums_plot

ggsave('./bbox_2fires/mo_sums_all_fil1_plot.png', dpi=600)

```

```{r}

rain23 <- read_stars('/Users/megansears/Documents/Repos/post-fire_rainfall/bbox_2fires/summertotal_2021_fil1.tif')

mapview(rain23)

```

