---
title: "Stage response analysis"
author: "Megan Sears"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_float: yes
    theme: journal
editor_options:
  chunk_output_type: console
---

```{r, include = F}

knitr::opts_chunk$set(echo = F,
                      message = F,
                      fig.width = 12,
                      fig.height = 6)

library(tidyverse)
library(plotly)
library(here)
library(ggplot2); theme_set(theme_bw(base_size = 20,
                                     base_family = "Arial"))
library(broom)
library(multcompView)
library(ggcorrplot)

```

# Read in data

```{r}

# # this is only for events > 5 cm
# response <- read_csv('./data/final/stage_mrms_response.csv') %>%
#   mutate(across(c(datetime_peak, datetime_min, start_time.y, end_time.y), mdy_hm)) %>%
#   mutate(date = mdy(date)) %>%
#   mutate(site = if_else(site == 'mont',
#                         'montgomery',
#                         site)) %>%
#   mutate(site = if_else(site == 'mich',
#                         'michigan',
#                         site))
#   
# 
# # read in SP
# sp <- read_csv('./data/final_model_inputs/sp_2000_2019_avg_catchments.csv')
# elev <- read_csv('./data/final_model_inputs/elev_range.csv')
# hypso <- read_csv('./data/final_model_inputs/hypso.csv')
# ic <- read_csv('./data/final_model_inputs/IC_mean.csv')
# inputs1 <- read_csv('./data/final_model_inputs/inputs1.csv')
# 
# inputs2 <- read_csv('./data/final_model_inputs/inputs2.csv') %>%
#   distinct(site, .keep_all = T) %>%
#   select(-c(relative_elev, relative_area))
#   
# ndvi_geo <- read_csv('./data/final_model_inputs/ndvi&geo.csv') %>%
#   rename(site = ID)
# 
# pwd <- read_csv('./data/final_model_inputs/pwd.csv') %>%
#   mutate(date = mdy(Date)) %>%
#   dplyr::select(-Date)
# 
# # join all model inputs together, except PWD b/c that's based on date
# df_list <- list(elev, hypso, ic, inputs1, inputs2, ndvi_geo, sp)
# 
# inputs <- reduce(df_list, left_join, by = c("site")) %>%
#   dplyr::select(-c(2:5, 9:13, 23:25, 38, 41:42)) %>%
#   dplyr::select(-c(28:30, 38:43))
# 
# write_csv(inputs, './data/final_model_inputs/inputs_combine.csv')

inputs <- read_csv('./data/final_model_inputs/inputs_combine.csv')

#response <- left_join(response, pwd, by = c('site', 'date'))

#all <- left_join(response, inputs, by = 'site')

```

# Inputs by fire & SP

```{r}

inputs <- inputs %>% 
  mutate(sp_cat = if_else(SP_mean > 60,
                          'high',
                          'low'))

# Get names of variables
numeric_cols <- names(inputs)[2:35]

# histogrms
plots <- map(numeric_cols, ~{
  ggplot(inputs, aes(x = .data[[.x]], fill=sp_cat)) +
    geom_density(alpha = 0.6) +
    facet_wrap(~fire, scales = "free") +
    theme_bw() +
    labs(title = paste(.x))
})

plots

shapiro_results <- inputs %>%
  select(-c(`%treated`, geology.x, geo_general.x)) %>%
  group_by(fire, sp_cat) %>%
  summarise(
    across(hypso25:SP_mean, ~ shapiro.test(.x)$p.value))

ggplot(param_sens, aes(x = value, fill = input_data)) +
  geom_density(alpha = 0.6) +
  facet_wrap(~param, scales = "free") +
  theme_bw(base_size = 20) +
  scale_fill_manual(values = c("#0047AB", "orange")) +
  theme(
    strip.background = element_blank(),
    panel.grid = element_blank(),
    legend.position = "bottom"
  )


# boxplots for all variables
plots <- map(numeric_cols, ~{
  ggplot(inputs, aes(x = fire, y = .data[[.x]], fill=sp_cat)) +
    geom_boxplot() +
    theme_bw() +
    labs(title = paste(.x))
})

# Print all plots
plots

```

# ANOVA 

```{r}
inputs_long <- inputs %>%
  select(-c(site, geo_general.x, geology.x)) %>%
  pivot_longer(!c(fire, sp_cat), 
               names_to = 'vars',
               values_to = 'vals')


tukey_results <- inputs_long %>%
  mutate(fire = as.factor(fire),
         sp_cat = as.factor(sp_cat)) %>%
  group_split(vars) %>%
  map(function(df) {
    # 2 way anova
    model <- aov(vals ~ fire * sp_cat, data = df)
    
    # Tukey HSD
    tukey_test <- TukeyHSD(model)
    
    # Tukey letters based on p val
    tukey_letters <- multcompLetters4(model, tukey_test)

    list(
      var = unique(df$vars),
      model = model,
      tukey = tukey_test,
      letters = tukey_letters
    )
  })


# Convert results into a tibble
tukey_df <- tibble(
  var = map_chr(tukey_results, "var"),
  model = map(tukey_results, "model"),
  tukey = map(tukey_results, "tukey"),
  letters = map(tukey_results, "letters")
)

# extract letters 
letters_all_vars <- tukey_df %>%
  mutate(
    letters_fire_sp_cat = map(letters, ~ {
      letters_vec <- .x$`fire:sp_cat`$Letters
      enframe(letters_vec, name = "group", value = "letter")})) %>%
  select(var, letters_fire_sp_cat) %>%
  unnest(letters_fire_sp_cat) %>%
  separate_wider_delim(group, ":", names = c('fire', 'sp_cat'))

# bring letters back into main df
inputs_tukey <- inputs_long %>%
  rename(var = vars) %>% 
  left_join(., letters_all_vars, by = c('var', 'fire', 'sp_cat')) %>%
  filter(!var %in% c('geo_coded', 
                     'geo_general_code', 
                     'max_elev', 
                     'min_elev', 
                     'slope'))

# find the max to place the letters in the plots
inputs_tukey <- inputs_tukey %>% 
  group_by(var, fire, sp_cat) %>%
  mutate(y_text = max(vals, na.rm = TRUE) * 1.01) %>%  # Slightly above max value
  ungroup()


ggplot(inputs_tukey, aes(x=fire, 
                         y=vals, 
                         fill=sp_cat)) + 
  geom_boxplot() +
  geom_text(aes(label = letter, y = y_text), 
            position = position_dodge(width = 0.75),  # Align with boxplots
            size = 6, 
            vjust = 0) + 
  facet_wrap(~var, scales='free_y', ncol=3) +
   scale_y_continuous(expand = expansion(mult = c(0.1, 0.15)))

ggsave('/Users/megansears/Documents/Repos/post-fire_rainfall/figures/SR_response/vars_boxplot.png',
       dpi=600,
       width=12,
       height=20)

##
corr_prep <- inputs %>%
  select(where(is.numeric))

corr_matrix <- cor(corr_prep, use = "complete.obs")

ggcorrplot(corr_matrix, method = "square", 
           hc.order = TRUE, # Hierarchical clustering order for better visualization
           type = "lower", 
           lab = TRUE, # Show correlation values in the squares
           lab_col = "black", # Color of the text labels
           lab_size = 3, # Size of the correlation values
           colors = c("blue", "white", "red")) +
  theme(
    plot.margin = margin(1, 1,1,1), # Adjust margins (top, right, bottom, left)
    axis.text.x = element_text(angle = 45, hjust = 1), # Rotate x-axis labels for better fit
    axis.text.y = element_text(hjust = 1) # Adjust y-axis label position
  )


```


```{r}
# Time varying inputs

```{r}

sp <- read_csv('./data/final_model_inputs/sp_2000_2019_avg_catchments.csv') %>%
    mutate(sp_cat = if_else(SP_mean > 60,
                          'high',
                          'low')) %>%
  select(site, sp_cat)
  
pwd <- read_csv('./data/final_model_inputs/pwd.csv') %>%
  mutate(date = mdy(Date)) %>%
  dplyr::select(-Date) %>%
  dplyr::select(date, lag_pwd, site)

fire <- inputs %>%
  select(site, fire)

info <- left_join(sp, fire, by ='site')

pwd <- left_join(pwd, info, by = 'site')

ggplot(pwd, aes(x=fire, fill=sp_cat, y=lag_pwd)) + geom_boxplot() + theme_bw()

# rainfall
response <- read_csv('./data/final/stage_mrms_response.csv') %>%
  mutate(across(c(datetime_peak, datetime_min, start_time.y, end_time.y), mdy_hm)) %>%
  mutate(date = mdy(date)) %>%
  mutate(site = if_else(site == 'mont',
                        'montgomery',
                        site)) %>%
  mutate(site = if_else(site == 'mich',
                        'michigan',
                        site))

response <- left_join(response, info, by ='site')

rain <- response %>%
  select(site, fire = fire.x,
         sp_cat, MI60 = MI60_mmhr.y, MI30 = MI30_mmhr.y,
         event_sum = event_sum_mm.y,
         duration = duration_hr.y)

ggplot(rain, aes(x=fire, fill=sp_cat, y=MI60)) + geom_boxplot() + theme_bw()
ggplot(rain, aes(x=fire, fill=sp_cat, y=MI30)) + geom_boxplot() + theme_bw()
ggplot(rain, aes(x=fire, fill=sp_cat, y=event_sum)) + geom_boxplot() + theme_bw()
ggplot(rain, aes(x=fire, fill=sp_cat, y=duration)) + geom_boxplot() + theme_bw()

```


```{r}
# # Stage rise
# 
# ```{r}
# 
# ggplot(all, aes(x=site, y=stage_rise_cm)) +
#   geom_boxplot() +
#   scale_y_log10() +
#   theme_bw(base_size=20)
# 
# # lag to peak
# lag2p <- all %>%
#   dplyr::select(site, datetime_peak, start_time.y, stage_rise_cm) %>%
#   mutate(lag2peak = datetime_peak - start_time.y) %>%
#   filter(!lag2peak<0)
# 
# ggplot(lag2p, aes(x=site, y=as.numeric(lag2peak))) +
#   geom_boxplot() +
#    scale_y_log10() +
#   theme_bw(base_size=20)
# 
# all <- all %>%
#   mutate(sp_cat = if_else(SP_mean > 60,
#                           'high',
#                           'low'))
# 
# ggplot(all, aes(x=sp_cat, y=stage_rise_cm, fill=fire)) +
#   geom_boxplot() +
#   #scale_y_log10() +
#   theme_bw(base_size=20)
# 
# lag2p_join <- lag2p %>%
#   dplyr::select(site, lag2peak)
# 
# all <- left_join(all, lag2p_join, by = 'site')
# 
# ggplot(all, aes(x=sp_cat, y=as.numeric(lag2peak), fill=fire)) +
#   geom_boxplot() +
#   theme_bw(base_size=20)


```




