---
title: "MRMS:MultiQPE,QPE, SPR"
author: "Megan Sears"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(
  echo = F,
  message = F, 
  warning  = F)

# load packages
library(R.utils) # to unzip the gz files
library(tidyverse)
library(lubridate)
library(raster)
#library(rgdal)
library(sf)
library(sp)
library(mapview)
library(terra)
library(tmap)
library(foreach)
library(doParallel)
library(magrittr)
library(beepr)

```

Create a bounding box to crop MRMS rasters (multi-QPE, QPE only, and SPR)

```{r}

# ETF watersheds - don't need right now
bbox <- vect('/Users/megansears/Documents/MRMS/bbox_2fires/bbox_2fires.shp')%>%
  terra::project(., '+proj=longlat +datum=WGS84 +no_defs')

# # All rain sensors for CPF, ETF, Bennett
# rain <- read_csv('./data/sensor_coords.csv') %>%
#   filter(type == 'rain') %>%
#   drop_na(y) %>%
#   st_as_sf(coords = c('x', 'y'), crs = 4326) %>%
#   st_transform(crs = st_crs(et_sheds))

# Bounding box based on rain sensors to crop MRMS data
bbox <- as(bbox, 'Spatial')
#bbox <- st_bbox(drowsy1)

# mapview(drowsy1)
# mapview(bbox)

# # Bounding box cuts off some points so expand it
# xrange <- bbox$xmax - bbox$xmin # range of x values
# yrange <- bbox$ymax - bbox$ymin # range of y values
# 
# bbox[1] <- bbox[1] - (0.1 * xrange) # xmin - left
# bbox[3] <- bbox[3] + (0.1 * xrange) # xmax - right
# bbox[2] <- bbox[2] - (0.1 * yrange) # ymin - bottom
# bbox[4] <- bbox[4] + (0.1 * yrange) # ymax - top
# 
# # Check bbox 
# mapview(bbox)



```

# 0. Unzip the grib2 files

```{r}

# Get rid of gz - unzip the grib2
setwd("/Users/megansears/Documents/MRMS/RQI/2021")

# Unzip all files
unzip <- list.files(path = '/Users/megansears/Documents/MRMS/RQI/2021', pattern = '.gz',
                  full.names = T)

unzip_all <- lapply(unzip, gunzip)


```

testing cropping before projecting

```{r}

test <- raster('/Users/megansears/Documents/MRMS/MultiSensor/2022/MultiSensor_QPE_01H_Pass2_00.00_20220501-120000.grib2')

crs(test) <- "+proj=longlat +datum=WGS84 +no_defs"
#crs(test) <- "ESRI:102009"

test1 <- raster::crop(test, bbox)

mapview(test1)

```

# 1. MutliQPE/QPE

Need to divide MultiQPE by QPE to get the correction used (this later gets applied to 2min data)

```{r}

setwd("/Users/megansears/Documents/MRMS")

# List files of the rasters in Multi Sensor QPE and radar QPE only
multi_rasters <- list.files("./MultiSensor/2021", pattern = ".grib2", full.names = TRUE)
folder2_rasters <- list.files("./QPE/2021", pattern = "grib2", full.names = TRUE)

# Multi_qpe / qpe and save raster
perform_division <- function(raster1, raster2, result_folder) {
  
  library(raster)
  
  # Extract the last 21 digits (datetime) from the file name
  last_21_digits1 <- substring(basename(raster1), max(nchar(basename(raster1)) - 20, 1))
  last_21_digits2 <- substring(basename(raster2), max(nchar(basename(raster2)) - 20, 1))
  
  if (last_21_digits1 == last_21_digits2) {
    r1 <- raster(raster1) 
    
    crs(r1) <- "+proj=longlat +datum=WGS84 +no_defs"
    
    r1 <- raster::crop(r1, bbox)
    
    r2 <- raster(raster2) 
    
    crs(r2) <- "+proj=longlat +datum=WGS84 +no_defs"
    
    r2 <- raster::crop(r2, bbox)
    
    result_raster <- r1 / r2 #divde Multi / QPE
    
    result_raster[is.na(result_raster)] <- 1 # if NA change to 1 (means no diff in precip bc 0/0)
    
    result_raster[is.infinite(result_raster)] <- 0
    
    # Save
    output_file <-
      file.path(result_folder, paste0("result_", last_21_digits1, ".tif"))
    
    writeRaster(result_raster, output_file, overwrite = TRUE)
  }
}

result_folder <- "/Users/megansears/Documents/MRMS/bbox_2fires/divide_2021"  # Path to the folder to save the resulting rasters

# Set the number of cores for parallel processing
num_cores <- 8

# parallel processing
cl <- makeCluster(num_cores)


clusterExport(cl, c("folder2_rasters", "result_folder", "perform_division", "bbox"))

# Division
parLapply(cl, multi_rasters, function(raster1) {
  # Extract the last 21 digits from the file name of raster1 (this is the datetime characters)
  last_21_digits1 <- substring(basename(raster1), max(nchar(basename(raster1)) - 20, 1))

  # Find matching rasters in folder2
  matching_rasters <- grep(last_21_digits1, folder2_rasters, value = TRUE)

  # Perform division for each matching raster
  mapply(perform_division, raster1, matching_rasters, MoreArgs = list(result_folder = result_folder))
})

# Stop
stopCluster(cl)

```

Get rid of .grib2 from all the filenames

```{r}

# Dir path where files are located
dir <- '/Users/megansears/Documents/MRMS/bbox_2fires/divide_2021'

# List the files in directory
file_list <- list.files(dir)

# Function to remove grib2 from filename
rename_files <- function(file) {
  new_name <- gsub(".grib2", "", file)
  file.rename(file.path(dir, file), file.path(dir, new_name))
}

# Apply renaming function
lapply(file_list, rename_files)

```

## Testing of above

```{r}

test_result <- raster("/Users/megansears/Documents/MRMS/MultiSensor_QPE_divide/2022/result_20220508-130000.tif")

test_qpe <- raster("/Users/megansears/Documents/MRMS/QPE/2022/RadarOnly_QPE_01H_00.00_20220508-130000.grib2") 

# Project the raster to a specific CRS if needed
test_qpe <- projectRaster(test_qpe, crs = '+init=EPSG:26913')

test_qpe <- raster::crop(test_qpe, bbox)

test_ms <- raster("/Users/megansears/Documents/MRMS/MultiSensor/2022/MultiSensor_QPE_01H_Pass2_00.00_20220508-130000.grib2") 

# Project the raster to a specific CRS if needed
test_ms <- projectRaster(test_ms, crs = '+init=EPSG:26913')

test_ms <- raster::crop(test_ms, bbox)

mapview(test_result, method = 'ngb') + mapview(test_qpe, method = 'ngb') + mapview(test_ms, method = 'ngb')

```

# 2. Project and crop the 2-min SPR data

Project and crop the 2-min SPR and save as tif so it can be multiplied by the correction later

```{r}

# Path to 2 min data
folder_path <- '/Users/megansears/Documents/MRMS/SPR/2021/2021_missing'
folder_path2 <- '/Users/megansears/Documents/MRMS/bbox_2fires/spr_crop_2021/missing'

# Get the list of GRIB2 files in the folder
files <- list.files(folder_path, pattern = "*.grib2", full.names = TRUE)

# Set the number of cores
num_cores <- 8

# PP settings
cl <- makeCluster(num_cores)
registerDoParallel(cl)

# project and crop function
process_file <- function(file) {
  
  # Read the GRIB2 file as a raster
  r <- raster(file)
  
  crs(r) <- "+proj=longlat +datum=WGS84 +no_defs"
  
  r <- raster::crop(r, bbox)
  
  # Save the raster as .tif
  new_file_name <- paste0(tools::file_path_sans_ext(basename(file)), "_processed.tif")
  new_file_path <- file.path(folder_path2, new_file_name)
  writeRaster(r, filename = new_file_path, overwrite = TRUE)
  
  # Remove (memory fills up if not)
  rm(r)
}

# PP with foreach
foreach(file = files, .packages = c("raster")) %dopar% {
  tryCatch({
    process_file(file)
  }, error = function(e) {
    message(paste("Error processing file:", file))
    message("Error message:", e)
  })
}

stopCluster(cl)

beep(sound=8)

```

# 3. Multiply!

Multiply the SPR (raw 2 min) by hour correction

First remove 'processed' from the projected and cropped SPR (2min) data

```{r}

dir <- '/Users/megansears/Documents/MRMS/bbox_2fires/spr_crop_2021/missing'

# Get the list of files in the folder
file_list <- list.files(dir, full.names = TRUE)

# Loop through each file and take off '_processed'
for (file_path in file_list) {

  file_name <- basename(file_path)

  if (grepl("_processed", file_name)) {
    
    new_file_name <- gsub("_processed", "", file_name)
    
    new_file_path <- file.path(dirname(file_path), new_file_name)
    
    file.rename(file_path, new_file_path)
    
    cat("Renamed:", file_name, "to", new_file_name, "\n")
  }
}

beep(sound=8)

```

Now multiply

```{r}

# Folder paths for the result (result of the divide) and precip rate rasters
result_folder <- "/Users/megansears/Documents/MRMS/bbox_2fires/divide_2021"
precip_folder <- "/Users/megansears/Documents/MRMS/bbox_2fires/spr_crop_2021/missing"
multiplied_folder <- "/Users/megansears/Documents/MRMS/bbox_2fires/2min_2021" # where the rasters will go

# List precip rate raster files
precip_files <- list.files(precip_folder, pattern = "^PrecipRate_.*\\.tif$", full.names = TRUE)

# Parallel processing
cl <- makeCluster(8)
registerDoParallel(cl)

get_result_hour <- function(precip_hour, precip_minute, precip_date) {
  n <- length(precip_hour)
  result_hour <- vector("character", n)

  for (i in 1:n) {
    if (precip_hour[i] == "23") {
      # Special case for "23" hour (since that will use the next day)
      if (precip_minute[i] == "00") {
        # If the minute is "00", use the same hour for the result hour
        result_hour[i] <- precip_hour[i]
      } else {
        # if not, set the result hour to "00"
        result_hour[i] <- "00"
        precip_date[i] <- as.character(as.Date(precip_date[i], format = "%Y%m%d") + 1)
        # Remove hyphens from date
        precip_date[i] <- gsub("-", "", precip_date[i])
      }
    } else if (precip_minute[i] == "00") {
      # If the minute is "00", use the same hour for the result hour
      result_hour[i] <- precip_hour[i]
    } else {
      # if not, increment the hour as before
      result_hour[i] <- sprintf("%02d", as.numeric(precip_hour[i]) + 1)
    }
  }

  return(list(result_hour = result_hour, precip_date = precip_date))
}

# Foreach for PP
foreach(precip_file = precip_files, .packages = c("raster")) %dopar% {
  
  # Get the last digits from the precip rate raster filename (datetime)
  precip_datetime <- substr(precip_file, nchar(precip_file) - 18, nchar(precip_file) - 4)
  
  # Extract the date, hour, and minute from the precip datetime
  precip_date <- substr(precip_datetime, 1, 8)
  precip_hour <- substr(precip_datetime, 10, 11)
  precip_minute <- substr(precip_datetime, 12, 13)
  
  # Get the result hour and updated precip date based on the minute of the precip datetime
  result_info <- get_result_hour(precip_hour, precip_minute, precip_date)
  result_hour <- result_info$result_hour
  precip_date <- result_info$precip_date
  
  # construct the result raster filename based on the date and result hour
  result_filename <- paste0("result_", precip_date, "-", result_hour, "0000.tif")
  result_file <- file.path(result_folder, result_filename)
  
  # Check if the files exist before reading
  if (file.exists(precip_file) && file.exists(result_file)) {
    # Read the precip rate raster
    precip_raster <- raster(precip_file)
    
    # Read result raster
    result_raster <- raster(result_file)
    
    # precip rate raster * the result raster
    multiplied_raster <- precip_raster * result_raster
    
    # Construct the output file path for the multiplied raster
    output_filename <- paste0("multiplied_", precip_datetime, ".tif")
    output_path <- file.path(multiplied_folder, output_filename)
    
    # output
    writeRaster(multiplied_raster, filename = output_path, format = "GTiff")
    
    cat("Raster multiplication completed for:", precip_file, "\n")
  } 
}

# Stop PP
stopCluster(cl)

beep(sound=8)

```

## Test above

```{r}

mult <- raster('/Users/megansears/Documents/MRMS/correctedSPR/drowsy_2023/multiplied_20230615-080800.tif')
corr <- raster('/Users/megansears/Documents/MRMS/MultiSensor_QPE_divide/drowsy_2023/result_20230615-090000.tif')
spr <- raster('/Users/megansears/Documents/MRMS/SPR/drowsy_2023/PrecipRate_00.00_20230615-080800.tif')

mapview(mult)

test1 <- corr*spr
test2 <- test1-mult
mapview(test2)

plot(test2)

mapview(mult) + mapview(corr) + mapview(spr)

```
